Sampling requirements to detect ecosystem change

### 2020-01-03 R/temporal-sampling.Rmd
added a few pieces of text

build_time_series <- function(mu=0,sigma=5,phi=0.5,shift_size=25,shift_time=50,max_time=100){

  ar1 <- vector(mode = 'numeric',max_time)
  ar1[1] <- 100
  for (t in 2:max_time){
    if(t == shift_time){ar1[t-1]=(ar1[1]-shift_size)}
    ar1[t] <- ar1[t-1] + phi*rnorm(1,mean=mu,sd = sigma)
  }
  return(ar1) 
}

@@

sample_size=10
params <- tibble(sigma=rep(seq(0.1,20,0.1),10))

@@

```{r different_methods, fig.cap='Theoretical results here',message=F,warning=F,echo=F}
# 4(or 6?) panel plot

par(mfrow=c(1,1))
# Sigma plot
sample_size=10
params <- tibble(sigma=rep(seq(0.1,20,0.1),100))

sample_size=10
params <- tibble(sigma=rep(seq(0.1,20,0.1),10))

>>>>

build_time_series <- function(mu=0,sigma=2,phi=0.5,shift_size=25,shift_time=50,max_time=100){

  ar1 <- vector(mode = 'numeric',max_time)
  ar1[1] <- 100
  shift_time = sample(5:95,size = 1)
  for (t in 2:max_time){
    if(t == shift_time){ar1[t-1]=(ar1[1]-shift_size)}
    ar1[t] <- ar1[t-1] + phi*rnorm(1,mean=mu,sd = sigma)
  }
  return(ar1) 
}

@@

sample_size=20
params <- tibble(sigma=rep(seq(0.1,20,0.1),10))

@@

```{r different_methods, fig.cap='Theoretical results here',message=F,warning=F,echo=F}

# Need to build a single plot comparing the three methods - look at probability of detection versus sample size... We would do this for a set of default parameters
